---
title: "Module 16"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Model Selection in General Linear Regression

Nested Comparisons: Compare with F test
Don't overfit model or lose confidence. 
```{r}

library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
z <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE)
m1 <- lm(data = z, height ~ age * gender)  # full model
m2 <- lm(data = z, height ~ age + gender)  # model without interactions
m3 <- lm(data = z, height ~ age)  # model with one predictor
m4 <- lm(data = z, height ~ 1)  # intercept only model

anova(m2, m1, test = "F")  # compares the reduced model without interactions (m2) to the full model with interactions (m1)

anova(m3, m2, test = "F")
```

Gender has a big explanatory effect on height.

Forward Selection 
Starts with intercept only and tests which of the predictor variables improves GOF best.
```{r}
m0 <- lm(data = z, height ~ 1)
summary(m0)
add1(m0, scope = . ~ . + age + weight + zombies_killed + years_of_education,
    test = "F")
m1 <- update(m0, formula = . ~ . + age + weight + zombies_killed + years_of_education,
    test = "F") # . ~ . Take my model and test out to see when it best fits
summary(m1)
m2 <- update(m1, formula = . ~ . + age)
summary(m2)

```
What you include in the model is what you add first. 

Backward Selection
Start with everything and then remove

``` {r}
m0 <- lm(data = z, height ~ age + weight + zombies_killed + years_of_education)
summary(m0)
drop1(m0, test = "F")
m1 <- update(m0, . ~ . - years_of_education)
summary(m1)
drop1(m1, test = "F")
m2 <- update(m1, . ~ . - zombies_killed)
summary(m2)
```
The two don't always land on the same results. Stop when all variables are significant 

## Model slection using AIC

```{r}
library(MASS)
stepAIC(m0, direction = "both")
```
``` 

Can't say anything about absolute fit of model. Not R^2 relative measures of fit and not absolute

```{r}

library(AICcmodavg)
print(aictab(list(m0, m1, m2), c("m0", "m1", "m2")), LL = FALSE)

```